\documentclass{article}
\title{Dungeons and Dragons 3.5 Campaign}
\author{Zac Dover}

\begin{document}
\maketitle

\section{Background}

Space Moose is aware of Boccob, the God of Magic, but has been more interested in revering Freddie Mercury since he heard \textit{Queen II}.

\section{The Events of August 17, 2014}
Space Moose finds himself aboard \textit{The Filthy Whore}, a ship traveling across an aquamarine saltwater sea, from Rektcliffe to Rocksfall, under the command of Captain Keating. \textit{The Filthy Whore} is on a course that Captain Keating calls ``Smuggler's Run''.

Space Moose, a human wizard, is quartered in a cabin in the starboard bow of the deck one level below the weather deck. He leaves this cabin and knocks on the door of the cabin to port. Ping answers the door, and Space Moose asks if Ping would like to find some alcohol and get drunk. Ping says that he doesn't drink, but he will come with Space Moose to find something to eat or something non-alcoholic to drink. Space Moose and Ping walk up the stairs to the weather deck, to find Douglas, a human bard, and Persis, a halfling, standing in the stern. Douglas is vomiting over the starboard bulwark. Soon, Muckroot and Blarg (a barbarian) join the party. Muckroot has a companion, Gummy, a crocodile. Persis has a companion, Barnabas, a raven. The party talks among itself and decides to explore ship, hunting for chickens for Gummy and alcohol for everyone\footnote{except Ping}.

The group explores the ship, and encounters a stout woman with a meat cleaver, a cook,  who tells them that there are no chickens in the room she's in and that they should find the pantry elsewhere. The party continues to explore the ship and ultimately enters a level below the level below the weather deck. It is almost completely dark. Only the raven and the crocodile and the gnomish druid can see anything.  This level of the ship is packed full of crates, with minimal room between them serving as thoroughfares. Near the stern of the ship, the party hears incomprehensible talk from behind the crates. The talk remains incomprehensible even to the wizard Space Moose, who has knowledge of languages, and to the gnomish druid, who knows, like, five languages. 

In the darkness near the stern of the ship, the party engages with an unknown party that strikes Muckroot's crocodile Gummy in the nose with a longsword. The blow is weak and does not kill Gummy. Persis remembers that she has an oil lamp, lights it, and the party is able to see in the cargo hold. The floor is revealed to be covered in pitch, to fight leaks. The aggressors look like lizard people: "Parasaurians," says Muckroot the gnomish druid.

Blarg the Barbarian intimidates the lizards, and Space Moose hits one of the lizard people with a quarterstaff. Persis hits the lizard person with Magic Missile for 5 damage. Ping inexplicably runs past a still-standing lizard-person without striking it at all. Blarg the Barbarian loses patience, charges to the fore, and swings a greatsword, narrowly missing Ping, who masterfully dodges. Space Moose is not so dextrous, and is hit in the belly with Blarg's greatsword after it passes through the lizard person. Space Moose is hit for -12, giving him -7HP. Space Moose falls into unconsciousness. 

The Captain and several crewmembers arrive, brandishing weapons. Douglas asks the Captain why militant lizard people were on the ship. Captain Keating and the crew take Space Moose upstairs. Blarg cuts off the leg of a lizard person to feed to Gummy the crocodile.

The party (minus Space Moose, who is mostly dead upstairs) finds two doors in the stern of the cargo hold. Blarg kicks through one of the doors, leaving a hole the size of a barbarian's foot in it.
On the other side of the door, Blarg can feel a metal bar under his foot. Blarg has found the ship's brig. Douglas the bard asks Blarg the barbarian what's inside the brig. Douglas looks inside and sees a shadowy figure. Douglas hears muttering from inside the brig. ``Hi there,'' Douglas says. ``You don't have any lizardy friends, do you?''

Meanwhile, Space Moose awakens in a room where the cook from earlier and a man are standing over him.

Back in the cargo hold, four more lizard people appear, amidships, apparently from nowhere. I mean that no one saw them show up. Everyone's back must have been turned or something.

Upstairs, the cook is pouring rancid salsa into Space Moose's mouth, which restores him to +4 health\footnote{This is a pretty good sentence.}. Space Moose sits up and leaves the room. Space Moose finds the Captain and offers to help in whatever way he can. When Space Moose finds the Captain, the Captain is in the cabin of a murdered man. The Captain asks Space Moose first if he can bring the dead man back to life (Space Moose can't), and then to fetch his friends. Space Moose says that he will not return alone to the cargo hold because he has HP4 and he is not stupid and he does not want to be killed. The Captain tells Space Moose to ask Morkin, the pilot of the ship, to get Maggie and Raynard to accompany him to the cargo hold. Space Moose sets off in search of Morkin the ship's pilot.

Back in the cargo hold, the crocodile Gummy snaps vainly at nothing\footnote{Good try, Gummy.}. Blarg tricks one of the parasaurians into cutting off the head of another parasaurian with what, in another context, might be called ``sweet dance moves''.

Upstairs, Space Moose finds Morkin piloting the ship. Space Moose describes the situation as comprehensibly as he can, and Morkin dispatches Raynard and Maggie to help. Maggie has two daggers, and Raynard has a spear\footnote{Raynard is totally taking a spear into close-quarters combat. Genius.}. Space Moose leads Maggie and Raynard to the cargo hold. Space Moose, Maggie, and Raynard are in the bow of the ship, and the rest of the party are visible to them in the stern, in the glow of the halfling's hooded lantern (and also, apparently, the gnomish druid did something that Annika described as "that lighting thing", which we'll document more completely later when we ask Laura what it was she did, if she even remembers by then, which she may not). The point is that the party is kind of split up: some of them are in the bow of the cargo hold, but most of them are in the stern of the cargo hold.

Ping punches the lizard people.

Persis gets well out of the range of the attacks of the lizard people and casts Magic Missile for 4 damage against a lizard person. This shears off the face of the lizard person, who sits down on the pitch hull and dies.

Douglas hits a lizard person for 1 damage. Douglas's lunge was executed a moment too soon, and it was executed with a shortsword, which is why the damage is so paltry. Also, Douglas is nauseated and may vomit at any moment. Also, the ship is moving the way a ship moves in water, which isn't helping Douglas not to vomit.

Space Moose asks Raynard and Maggie to fight the parasaurians\footnote{This is a pretty good sentence, too.}. Maggie charges forward and slaps a parasaurian. It dies, but it may not have died from the slap. It might have been dying anyway. But Maggie at least makes her allegiance known by the slap. She is not fighting for the parasaurians.

Muckroot summons Nature's Ally, a venomous viper, inside the brig\footnote{There was a brief discussion about the distinction between the words ``poisonous'' and ``venomous'', and it was agreed that the viper was venomous and not poisonous. Good discussion.``Who knows?'' Annika says. ``Maybe viper meat is also poisonous.'' This is a question that will be solved by future generations who are equipped with more complete biological science. (We couldn't find the answer within 40 seconds of Googling, so we gave up.)}. The magic-sensitive members of the party sense a failed spell, like a missed golf-ball (``whiff''), from within the brig. Clearly the muttering shadowy figure has failed to dispel Nature's Ally.

Persis casts Magic Missile into the brig.

Douglas fails to hit the shadowy figure in the brig.

The gnome does nothing effective.

Blarg hits a crate.

Ping fails to hit anything.

Persis listens at the door and hears nothing.

The viper shoots fire and sets the hull of the ship on fire.

Space Moose sends Maggie to stab the parasaurian to death. Maggie climbs on top of the parasaurian and stabs it with both of her daggers, killing it.

Everything in the cargo hold is on fire. The party runs upstairs. The party reports the fire to the Captain. The Captain, trailed by some of his crew, goes downstairs.

The Captain returns upstairs, and enters into a quasi-legal dispute with Space Moose and Douglas about the etiology of the fire and the contents of the brig. The Captain does not believe that there was anything in the brig at the time, and raises the possibility that someone in the party conjured the fish people. 

Space Moose and Blarg learn that a figure under the sheet was not the shadowy figure in the brig but the primary passenger on the ship, the man in whose cabin Space Moose earlier found the Captain.

As thinkers dither, Blarg gets bored.

Blarg turns to watch the sunset over the bulwarks, and Space Moose accompanies him.

\section{The Events of 06 Sep 2014}

It is the following day.

The party retrieves the unconscious, probably drunk body of Douglas and moves to the bottom story of the ship to investigate the brig.

There's a body in the brig under a sheet. The body is that of a middle-aged man who has been stabbed multiple times in the stomach before his throat was cut.

Blarg kicks through another door, finding the pantry. The party cheers, saying "Yay!". Blarg wonders at the meat in the pantry because there's a corpse stored handily nearby.

Muckroot says "Hey, are there any chickens there?" Nope. "What about meat?" There is a crate of salted legs. Muckroot takes one salted leg. Persis asks for a salted leg. Muckroot gets a salted leg for Persis.

Ping suggests that the party go talk to the Captain. The party goes back upstairs to look for the Captain. They can't find the Captain.

Blarg goes to the Captain's quarters. Space Moose goes with Blarg. Blarg hammers on the door and Space Moose asks why there was a corpse in the brig. The Captain says that the brig was not locked, perhaps irrelevantly.

The Captain says ``My business is not your concern. The ship was on fire, that is your concern.''

The party tries pathetically to convince the Captain to come clean about who the passenger is. 

Blarg shoves his way through the Captain's door as the Captain closes the door. ``Blarg not leaving until Blarg get story,'' says Blarg.

Space Moose knocks on the door. Blarg attempts to open the door, but Reynard is leaning against it. The First Mate threatens Blarg, resting his hammer on Blarg's arm.

The Captain reveals that magic was sensed twice on the ship yesterday. The lizard people then showed up. The Captain says ``I am willing to concede that you were not responsible for the lizard people showing up. There is still stuff that's not your business. One of my crew sensed teleportation magic. Someone was capable of teleportation.''

Space Moose asks who the dead man is. The Captain says that he supposes it's a fair question and that the man was a messenger. Obviously, says the Captain, someone wanted the message not to be delivered.

Space Moose asks where the message is.

The Captain says that he wants the party to deliver the message.

Space Moose tells an entertaing story of wrestling to Blarg so that Blarg isn't so bored that he wanders off. The entire party goes to the mysterious man's room. Space Moose and Blarg stay outside the room, talking of wrestling, while the party goes inside the mysterious messenger's room. There is a single bed, and the cabin is better decorated than the rest of the ship. A wooden foot locker is present. Several personal effects are scattered about the cabin. The personal effects include clothing. One of the articles of clothing has an emblem on it. The emblem is made of five different emblems: scales, sword, potion bottle, saw, coin.

Blarg has uncanny dodge.

Persis brings the be-emblemed garment to Space Moose, who recognizes it as something associated with Rocksfall.

The party except for Blarg clears the room. Blarg takes a crowbar out and pries the lockbox open. Somehow there is fire in the box.

Blarg opens the door and yells for water. Persis hands Blarg a waterskin and Blarg uses it to put out the fire.

Muckroot looks at the contents of the box: wet charred muck. Nothing but charred muck is in the box.

Everyone takes a spot check. Under the bed, there's a small emptied case. The lock on it has been broken. A couple of sets of clothing. A book, a fiction about hero of Rectcliff. The book is missing any covering and title. Its first line is ``Mere hours had passed since the storm had finally abated.''

Down in the brig, the body is wearing plain black boots. The body is dressed in gray and black. He has a small purse in his left pocket. 7 coppers and 1 silver are in the purse.

The party strips the body. Space Moose plays dress-up with the removed clothing.The body has a penis. It's a ``fairly nice'' penis. It has a bruise on it, possibly, says the DM, from where the character fell\footnote{What?}.

He has both balls.

He also has several tattoos. They are simple and decorative lines.

The character is South Asian-ish.

Everybody goes to the papryus crate and Persis gets some charcoal and makes some drawings of the tattoos on the body of the man.

The party returns to the Captain's quarters. Maggie stands guard outside the cabin. The Captain says that a ship was sighted briefly before it disappeared behind a small island. Upon returning upstairs, the party notices that a mist has descended and the horizon is no longer visible. The Captain informs you that everyone who can bear weapons is expected to. 

The Captain looks at the narrative of Rectcliffe. `` `Erroneous questions never helped a man swim' said the gaunt drow.'' he says.

In the VIP room, Ping notices that the handles on the outside of the room's doorwere removed a long time ago. On the inside, the handle is slightly bent, as though it had been opened by force.

Persis look at the mist. It's mist. 

Muckroot goes upstairs with her crocodile. She rolls a spot check, gets a 20, and sees extra mist.

Ping looks out the window and sees something that no one else sees. It was a small pouch that was pinned above the window. Ping opens the pouch. A single piece of folded papyrus is in the bag. It is written in a language that Space Moose recognizes as Celestial.

Everyone made a copy of the parchment.

``Blarg does not care for parchment.'' says Blarg, as he surrenders his copy of the Celestial script to give to the Captain for examination.

The Captain reads the message and frowns. The frown goes away and the Captain says ``Thank you very much. This will make it easier to clear my name.''

The party asks what the message says. The Captain says that he cannot read the message. The party asks why the Captain thinks that he can clear his name. The Captain says that it is because the message proves that he still has a message to deliver.

Persis asks are we there yet, and the Captain says that we are three days from Rocksfall.

Muckroot reads from the last page. The last line is ``It was all a dream. You have now successfully installed Java.''

Space Moose begins writing his own book\footnote{``Spewing diarrhea from his burning anus, Gardegar screamed in the ancient tongue.''}.

Blarg goes to listen to the mist. Persis hangs out with Blarg. Blarg hears a ship behind The Filty Whore. Blarg tells the party that there is another ship out in the mist.

Barnabas the Raven flies around the boat. Gummy the Crocodile goes overboard to see what he can see.

Barnabas the Raven has been killed. A clump of feathers falls to the deck. Persis starts crying.

Gummy knows that the water is bad.

A cry from the crow's nest is followed by a body hitting the deck.

The party fights an air elemental. Space Moose strikes the air elemental for 3. Persis hits for 5. Muckroot misses. Gummy tail-whips for 11. Ping grapples with the air elemental, successfully holding it. Blarg missed. Space Moose missed. Persis hits for 4. A second air elemental appears. Muckroot misses. Blarg takes 6 damage. The Captain does 3 damage to the air elemental. Space Moose hits for 1. Muckroot casts flare and dazzles the air elemental. A lantern is flung to the captain, but it catches the air elemental. The air elemental turns into a tornado of fire. The mainsail bursts into flame.

The party, except for the unconscious bard Douglass, stands staring at the flaming sail with faces of \textit{oh shit}.



\end{document}
